---
title: "R Notebook"
output: html_notebook
---

```{r}
nba = read.csv("../R-project/NBASeasonData.csv")
nba = subset(nba, Player!=0)
```

As the dataset spans almost 30 years, the methods of collecting data aren't consistent. Therefore, we are using data from 2013 onwards.


There have also been major rule changes that have lead to changes in stats for the seasons


We also get rid of null values and records with insufficient data.
```{r}
nba_sub = subset(nba,Year>=2013)
nba_sub = subset(nba_sub,Player!=0)
```
We want to see whether there's been an increase in 3pt attempts after a certain year, or player entering the league
We do this by using thr 3Par stat.
```{r}
y1978 = subset(nba,Year==1978)
y1979 = subset(nba,Year==1979)
y1980 = subset(nba,Year==1980)
y1981 = subset(nba,Year==1981)
y1982 = subset(nba,Year==1982)
y1983 = subset(nba,Year==1983)
y1984 = subset(nba,Year==1984)
y1985 = subset(nba,Year==1985)
y1986 = subset(nba,Year==1986)
y1987 = subset(nba,Year==1987)
y1988 = subset(nba,Year==1988)
y1989 = subset(nba,Year==1989)
y1990 = subset(nba,Year==1990)
y1991 = subset(nba,Year==1991)
y1992 = subset(nba,Year==1992)
y1993 = subset(nba,Year==1993)
y1994 = subset(nba,Year==1994)
y1995 = subset(nba,Year==1995)
y1996 = subset(nba,Year==1996)
y1997 = subset(nba,Year==1997)
y1998 = subset(nba,Year==1998)
y1999 = subset(nba,Year==1999)
y2000 = subset(nba,Year==2000)
y2001 = subset(nba,Year==2001)
y2002 = subset(nba,Year==2002)
y2003 = subset(nba,Year==2003)
y2004 = subset(nba,Year==2004)
y2005 = subset(nba,Year==2005)
y2006 = subset(nba,Year==2006)
y2007 = subset(nba,Year==2007)
y2008 = subset(nba,Year==2008)
y2009 = subset(nba,Year==2009)
y2010 = subset(nba,Year==2010)
y2011 = subset(nba,Year==2011)
y2012 = subset(nba,Year==2012)
y2013 = subset(nba,Year==2013)
y2014 = subset(nba,Year==2014)
y2015 = subset(nba,Year==2015)
y2016 = subset(nba,Year==2016)
y2016 = subset(y2016,Player!=0)

three_point_average=c(mean(y1978$X3PAr),mean(y1979$X3PAr),mean(y1980$X3PAr),mean(y1981$X3PAr),mean(y1982$X3PAr),mean(y1983$X3PAr),mean(y1984$X3PA),mean(y1985$X3PAr),mean(y1986$X3PAr),mean(y1987$X3PAr),mean(y1988$X3PAr),mean(y1989$X3PAr),mean(y1990$X3PAr),mean(y1991$X3PAr),mean(y1992$X3PAr),mean(y1993$X3PAr),mean(y1994$X3PAr),mean(y1995$X3PAr),mean(y1996$X3PAr),mean(y1997$X3PAr),mean(y1998$X3PAr),mean(y1999$X3PAr),mean(y2000$X3PAr),mean(y2001$X3PAr),mean(y2002$X3PAr),mean(y2003$X3PAr),mean(y2004$X3PAr),mean(y2005$X3PAr),mean(y2006$X3PAr),mean(y2007$X3PAr),mean(y2008$X3PAr),mean(y2009$X3PAr),mean(y2010$X3PAr),mean(y2011$X3PAr),mean(y2012$X3PAr),mean(y2013$X3PAr),mean(y2014$X3PAr),mean(y2015$X3PAr),mean(y2016$X3PAr))
```

