---
title: "R Notebook"
output: html_notebook
---

```{r}
nba = read.csv("../R-project/NBASeasonData.csv")
nba = subset(nba, Player!=0)
```

As the dataset spans almost 30 years, the methods of collecting data aren't consistent. Therefore, we are using data from 2013 onwards.


There have also been major rule changes that have lead to changes in stats for the seasons


We also get rid of null values and records with insufficient data.
```{r}
nba_sub = subset(nba,Year>=2013)
nba_sub = subset(nba_sub,Player!=0)
```
We want to see whether there's been an increase in 3pt attempts after a certain year, or player entering the league
We do this by using thr 3Par stat.

```{r}
#discaring the NA and empty 3Par stats
three_pt_stats = nba[!(is.na(nba$X3PAr) | nba$X3PAr==""), ]

#separating the stats for all the years
y1978 = subset(three_pt_stats,Year==1978)
y1979 = subset(three_pt_stats,Year==1979)
y1980 = subset(three_pt_stats,Year==1980)
y1981 = subset(three_pt_stats,Year==1981)
y1982 = subset(three_pt_stats,Year==1982)
y1983 = subset(three_pt_stats,Year==1983)
y1984 = subset(three_pt_stats,Year==1984)
y1985 = subset(three_pt_stats,Year==1985)
y1986 = subset(three_pt_stats,Year==1986)
y1987 = subset(three_pt_stats,Year==1987)
y1988 = subset(three_pt_stats,Year==1988)
y1989 = subset(three_pt_stats,Year==1989)
y1990 = subset(three_pt_stats,Year==1990)
y1991 = subset(three_pt_stats,Year==1991)
y1992 = subset(three_pt_stats,Year==1992)
y1993 = subset(three_pt_stats,Year==1993)
y1994 = subset(three_pt_stats,Year==1994)
y1995 = subset(three_pt_stats,Year==1995)
y1996 = subset(three_pt_stats,Year==1996)
y1997 = subset(three_pt_stats,Year==1997)
y1998 = subset(three_pt_stats,Year==1998)
y1999 = subset(three_pt_stats,Year==1999)
y2000 = subset(three_pt_stats,Year==2000)
y2001 = subset(three_pt_stats,Year==2001)
y2002 = subset(three_pt_stats,Year==2002)
y2003 = subset(three_pt_stats,Year==2003)
y2004 = subset(three_pt_stats,Year==2004)
y2005 = subset(three_pt_stats,Year==2005)
y2006 = subset(three_pt_stats,Year==2006)
y2007 = subset(three_pt_stats,Year==2007)
y2008 = subset(three_pt_stats,Year==2008)
y2009 = subset(three_pt_stats,Year==2009)
y2010 = subset(three_pt_stats,Year==2010)
y2011 = subset(three_pt_stats,Year==2011)
y2012 = subset(three_pt_stats,Year==2012)
y2013 = subset(three_pt_stats,Year==2013)
y2014 = subset(three_pt_stats,Year==2014)
y2015 = subset(three_pt_stats,Year==2015)
y2016 = subset(three_pt_stats,Year==2016)

#calculating the average 3Par stat for each year across all the players
three_point_average=c(mean(y1978$X3PAr),mean(y1979$X3PAr),mean(y1980$X3PAr),mean(y1981$X3PAr),mean(y1982$X3PAr),mean(y1983$X3PAr),mean(y1984$X3PA),mean(y1985$X3PAr),mean(y1986$X3PAr),mean(y1987$X3PAr),mean(y1988$X3PAr),mean(y1989$X3PAr),mean(y1990$X3PAr),mean(y1991$X3PAr),mean(y1992$X3PAr),mean(y1993$X3PAr),mean(y1994$X3PAr),mean(y1995$X3PAr),mean(y1996$X3PAr),mean(y1997$X3PAr),mean(y1998$X3PAr),mean(y1999$X3PAr),mean(y2000$X3PAr),mean(y2001$X3PAr),mean(y2002$X3PAr),mean(y2003$X3PAr),mean(y2004$X3PAr),mean(y2005$X3PAr),mean(y2006$X3PAr),mean(y2007$X3PAr),mean(y2008$X3PAr),mean(y2009$X3PAr),mean(y2010$X3PAr),mean(y2011$X3PAr),mean(y2012$X3PAr),mean(y2013$X3PAr),mean(y2014$X3PAr),mean(y2015$X3PAr),mean(y2016$X3PAr))

#Plotting the acerage percentage of attempted shots that were 3 pointers vs. the years
plot(c(1978:2016),three_point_average,main = "Variation in percentage of 3 pointers attempted",xlab = "Year", ylab = "Percentage of 3 pointers attempted", type = "h", col = "blue")

```

Trying to see if there is a relation between shooting percentage and height

```{r}
#discaring the NA and empty shooting percentage and height stats
shooting_stats = subset(nba_sub,(!is.na(nba_sub$TS.) & nba_sub$TS.!="" & !is.na(nba_sub$Height) & nba_sub$Height!=""))

zero_to_ten=subset(shooting_stats,(TS.>=0.0 & TS.<0.1))
ten_to_twenty=subset(shooting_stats,(TS.>=0.1 & TS.<0.2))
twenty_to_thirty=subset(shooting_stats,(TS.>=0.2 & TS.<0.3))
thirty_to_forty=subset(shooting_stats,(TS.>=0.3 & TS.<0.4))
forty_to_fifty=subset(shooting_stats,(TS.>=0.4 & TS.<0.5))
fifty_to_sixty=subset(shooting_stats,(TS.>=0.5 & TS.<0.6))
sixty_to_seventy=subset(shooting_stats,(TS.>=0.6 & TS.<0.7))
seventy_to_eighty=subset(shooting_stats,(TS.>=0.7 & TS.<0.8))
eighty_to_ninety=subset(shooting_stats,(TS.>=0.8 & TS.<0.9))
ninety_to_hundred=subset(shooting_stats,(TS.>=0.9 & TS.<1.0))

View(zero_to_ten)
View(ten_to_twenty)
View(twenty_to_thirty)
View(thirty_to_forty)
View(forty_to_fifty)
View(fifty_to_sixty)
View(sixty_to_seventy)
View(seventy_to_eighty)
View(eighty_to_ninety)
View(ninety_to_hundred)

#ten_to_twenty=shooting_stats[shooting_stats$TS.>=0.1 & shooting_stats$TS.<0.2]

#twenty_to_thirty=shooting_stats[shooting_stats$TS.>=0.2 & shooting_stats$TS.<0.3]

#thirty_to_forty=shooting_stats[shooting_stats$TS.>=0.3 & shooting_stats$TS.<0.4]

#forty_to_fifty=shooting_stats[shooting_stats$TS.>=0.4 & shooting_stats$TS.<0.5]

#fifty_to_sixty=shooting_stats[shooting_stats$TS.>=0.5 & shooting_stats$TS.<0.6]

#sixty_to_seventy=shooting_stats[shooting_stats$TS.>=0.6 & shooting_stats$TS.<0.7]

#seventy_to_eighty=shooting_stats[shooting_stats$TS.>=0.7 & shooting_stats$TS.<0.8]

#eighty_to_ninety=shooting_stats[shooting_stats$TS.>=0.8 & shooting_stats$TS.<0.9]

#ninety_to_hundred=shooting_stats[shooting_stats$TS.>=0.9 & shooting_stats$TS.<1.0]

mean_heights=c(mean(zero_to_ten$Height),mean(ten_to_twenty$Height),mean(twenty_to_thirty$Height),mean(thirty_to_forty$Height),mean(forty_to_fifty$Height),mean(fifty_to_sixty$Height),mean(sixty_to_seventy$Height),mean(seventy_to_eighty$Height),mean(eighty_to_ninety$Height),mean(ninety_to_hundred$Height))

plot(c(0.0,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9),mean_heights)
```